The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-04-21 paper/ms.tex
new version for resubmission

The Bullet Cluster (\bulla) provided a new kind of observational
evidence for the existence of dark matter
\citep{Markevitch2004,Clowe2006}. Since then it has been used to test
the Cold Dark Matter (CDM) paradigm itself by quantifying different
aspects such as the expected displacement between the dominant dark
matter and baryonic component in a $\Lambda$CDM Universe
\citep{ForeroRomero2010}, the substructure velocity required to
produce such displacement
\citep{Milosavljevic2007,Springel2007,Mastropietro2008} and its
abundance in large N-body cosmological simulations
\citep{Hayashi2006,Lee2012, Thompson2012}. It has also been used to
constrain the dark matter particle self-interaction cross section and
to explore possible extensions to the concordance cosmological model
\citep{Farrar2007,Lee2010}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_2.pdf}
\end{center}
\caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
  geometry of the bullet encounter. The left
  panel corresponds to clusters and the right panel to groups. 
  The weak redshift evolution of the structure in these planes
  allows us to include halos at all redshifts to construct these figures.
  The three rectangles (continuous, dashed, dashed-dotted)
  delimit stages of interest in a head-on collision as described in
  Section \ref{sec:geometry}.}
\label{fig:geometry}
\end{figure*}

@@

The first region has $\mu<-0.9$ and $D_{\rm off}>0.6$, which
locates the systems where a head-on collision has just started. The
second region has $\mu>0.9$ and $D_{\rm off}<0.6$; at this stage
the collision continues after the first crossing of the host's
center. The low number of halos with radial infalling velocities and
displacements $D_{\rm off}>0.6$ suggests that this the maximum range of
radii for the apogee.  The third region corresponds to $\mu<-0.9$
and $D_{\rm off}<0.6$ that is the the secondary infall after apogee.

@@

\bibliographystyle{apj}
%\bibliography{references} 
\begin{thebibliography}{28}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

>>>>

The Bullet Cluster (\bulla) provided a new kind of observational
evidence for the existence of dark matter
\citep{Markevitch2004,Clowe2006}. Since then it has been used to test
the Cold Dark Matter (CDM) paradigm itself by quantifying different
aspects such as the expected displacement between the dominant dark
matter and baryonic component in a $\Lambda$CDM Universe
\citep{ForeroRomero2010}, the substructure velocity required to
produce such displacement
\citep{Milosavljevic2007,Springel2007,Mastropietro2008} and its
abundance in large N-body cosmological simulations
\citep{Hayashi2006,Lee2010, Thompson2012}. It has also been used to
constrain the dark matter particle self-interaction cross section and
to explore possible extensions to the concordance cosmological model
\citep{Farrar2007,Lee2012}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_2.pdf}
\end{center}
\caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
  geometry of the bullet encounter. The left panel corresponds to
  clusters and the right panel to groups.  The weak redshift evolution
  of the structure in these planes allows us to include halos at all
  redshifts to construct these figures. The three rectangles
  (continuous, dashed, dot-dashed) roughly delimit stages of interest
  in a head-on collision (initial infall, first crossing until apogee,
  return after apogee) as described in Section 
  \ref{sec:geometry}.}  
\label{fig:geometry}
\end{figure*}

@@

The first region (continuous rectangle) has $\mu<-0.9$ and $D_{\rm
  off}>0.6$, which locates the systems where a head-on collision has
just started. The second region (dashed rectangle) has $\mu>0.9$ and
$D_{\rm off}<0.6$; at this stage the collision continues after the
first crossing of the host's center. The low number of halos with
radial infalling velocities and displacements $D_{\rm off}>0.6$
suggests that this the maximum range of radii for the apogee.  The
third region (dot-dashed rectangle) corresponds to $\mu<-0.9$ and
$D_{\rm off}<0.6$ that is the the secondary infall after apogee.

@@

\bibliographystyle{apj}
\begin{thebibliography}{28}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
